\subsection{A fitted covering law replaces the imposed photon closure}
\label{sec:coregulated_covering}

The quadratic closure of Section~\ref{sec:physical_visibility_closure}
reproduces the stacked dense-fraction sequence but is imposed at the
photon-partition level. Decomposing it against the lifecycle's own physics
shows that ordinary flux competition---the envelope-intercepted engine
photons against stellar and escaped-nuclear illumination of the diffuse
gas---supplies an emergent source-level exponent of only 0.5--0.9 of the
required two powers of $D$, while the legacy covering fraction, drawn from
the nuclear Thomson depth alone, carries 0.09 powers. The missing factor is
therefore an interception law: the covering odds must be co-regulated with
the engine.

We implement this as a one-line replacement of the covering model. With
$x \equiv L_{\nu,\mathrm{engine}}(2500\,\text{\AA}) /
L_{\nu,\star}(2500\,\text{\AA})$ the intrinsic (pre-attenuation,
pre-covering) engine-to-host contrast, the covering odds are
\begin{equation}
  \frac{C}{1-C} = k\,x^{\gamma}
  \label{eq:covering_law}
\end{equation}
with lognormal per-halo scatter (0.35 dex). Both continuum terms are
upstream of every observable the law affects, so
Equation~\ref{eq:covering_law} is not circular. A 12-point joint scan over
$\gamma\in\{1.5,2,2.5,3\}$ and $k\in\{0.5,1,2\}$, scoring the physical
photon partition against the four stack-inverted dense fractions plus the
demographic fit, selects $(\gamma,k)=(2,1)$ as a clear interior optimum:
covering odds equal to the \emph{squared} contrast with unit
normalization---50 percent covering at engine--host parity.

Under the fitted law, the raw photon partition, with no imposed closure
anywhere, reproduces the stack sequence: predicted dense fractions 0.951,
0.907, 0.754, and 0.451 against the inverted 0.981, 0.901, 0.738, and 0.086
(the bLRD interval extends to 0.658), with $\chi^2=1.6$--2.0 under the
declared 0.05 systematics floor, versus 3.7--9.9 for every candidate under
the legacy covering. The result is seed-stable. Simultaneously and without
retuning, the demographic $\chi^2$ improves from 12.24 to 5.5, with the
three $z<8$ bins inside one sigma; the H$\alpha$ offset against the
UV-matched public control improves from $+0.89$ to $+0.64$ dex; and the
RUBIES broad-width distribution distance improves from 0.413 to 0.354, with
the matched population shifting to Compton-thick Thomson depths
($\tau_{\rm e}\simeq2.3$) so that the widths become substantially
electron-scattering broadened rather than purely virial.

The stacked data constrain only four subtype medians, and the fitted
physical chain reproduces them while its source-level exponent remains
$\sim$0.7. The quadratic of Section~\ref{sec:physical_visibility_closure} is
therefore the subtype-median shadow of Equation~\ref{eq:covering_law}
rather than a fundamental photon-partition law. Structurally, the odds form
and the parity anchor are derivable: any engine-built, host-cleared
equilibrium $\dot C=(1-C)B-CG$ equilibrates at $C/(1-C)=B/G$, and the
momentum-flux ratio at the shared host interface,
$(L_e/c)/(\dot p_{\rm SN}\,\mathrm{SFR})$, evaluates to order unity at
$x=1$ from standard constants alone. One power of $x$ follows from this
momentum bookkeeping; the second, attributed to radiation-confined clump
survival against host ablation, remains an order-of-magnitude candidate. A
time-resolved implementation of the build/clear dynamics shows the
stationary law is its fast-relaxation limit and that the data bound the
covering relaxation time at $\lesssim30$~Myr: slower envelopes retain
fossil covering in fading engines, repopulating the blue subtype class with
dense sources and degrading both the stack and demographic comparisons
monotonically. This bound is consistent with the $\sim$10~yr dynamical time
at the envelope scale.

The fitted law is falsifiable on four fronts. (i) Blue-continuum LRDs
should be systematically more X-ray transmitting and more variable than red
LRDs at matched bolometric luminosity, with a steepened
variability--subtype gradient. (ii) Object-level line-ratio scatter within
a continuum subtype should exceed the tight locus implied by a
deterministic $D^2$ law, reflecting the covering scatter. (iii) The
covering saturates near $x\simeq14$, so the reddest sources should be
homogeneous in covering-driven marks. (iv) No thick hysteresis loop should
appear in the variability--color plane; observing one would contradict the
fast-equilibration hierarchy, not merely a parameter choice.

Finally, the co-regulated covering resolves the character of the
high-redshift demographic residual. At $z\simeq9.5$ the intrinsic
$M_{\rm UV}<-18.5$ nuclear-active population exceeds the reported density
by a factor of $\sim$27, but most of it carries unbuilt envelopes and blue
continua and is removed by the V-shape color gate. Rescaling that single
gate within transparent limits swings the $z=9.5$ prediction from a
$2\sigma$ deficit to an $8\sigma$ excess while moving the $z\le7.5$ bins by
well under one sigma. The $z\simeq9.5$ bin is therefore a thermometer of
color-selection completeness rather than a formation constraint, and no
additional formation channel is required by current number densities. The
model's corresponding prediction is compositional: the real $z>8.5$ LRD
population should be dominated by blue-continuum, low-covering compact
sources, a statement testable by a subtype census and by injection/recovery
completeness for blue compact templates.
